Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-11-24 Scripts/Initial_Analysis.Rmd
William's comments and changes proportion estimations

@@

#### Both plots for tresh one

plot <- ggplot() +
  geom_area(data = subset(plot_data, level == "eez"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            alpha= 0.8,
            size=0.5,
            colour="black"
  )  +
  geom_area(data = subset(plot_data, level == "stock"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            alpha= 0.8,
            size=0.5,
            colour="black"
  )  +
  # geom_line(data = subset(plot_data, metric == "com_sum"),
  #           aes(
  #             x = as.numeric(taxon_emer),
  #             y = total,
  #             fill = level
  #           ),
  #           colour="grey30",
  # )  +
  # geom_text(data = subset(plot_data, metric == "com_sum"),
  #           aes(
  #             x = 2037,
  #             y = total+5,
  #             label = label
  #           ),
  #           size = 3,
  #           colour="grey30",
  #           hjust=0.6,
  # )  +
  facet_wrap(~my_facet,
             scales = "free") + 
  scale_y_continuous("",
                     expand = c(0,0)
                     ) +
  scale_x_continuous("Time of emergence",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     label = c(seq(2000,2075,25),">2100"),
                     expand = c(0, 0)
  ) +
  my_ggtheme_p() +
  theme(
    legend.position = "right",
    strip.text.x = element_blank()
  ) +
  guides(fill=guide_legend(title= "Level")) +
  scale_fill_viridis(discrete = T,
                     begin = 0.1, 
                     end = 0.7,
                     labels = c("EEZs","Stocks")
  ) +
  ggsave("./Figures/cumu_per_freq.png",
  width = 12,
  height = 7,
  units = "in"
  )

@@

Eez_hist <- Eme_Res %>% 
  group_by(eezid,eez_name = sf_eez_name) %>% 
  left_join(Eez_centroid) %>% 
  filter(tresh == tresh_list[i]) %>% 
  group_by(latitude) %>% 
  summarise(
    number = n()
  ) %>% 
  group_by() %>% 
  mutate(RMean = rollmean(x = number, 
                          10, 
                          align = "center", 
                          fill = number
  )
  ) %>% 
  mutate(lab="lab") %>% 
  ggplot() +
  geom_area(
    aes(
      x = latitude,
      y = RMean,
      fill = lab,
      color = lab
    )
  ) +
  coord_flip() +
  scale_x_continuous("",
    limits = c(-50,80),
    breaks = c(-50,0,50,80)
  ) +
  scale_y_continuous(
    "Emerging stocks",
    limits = c(0, 124),
    breaks = c(0,62,124)

  ) +
  scale_fill_viridis(option="magma", discrete = T, begin = 0.7) +
  scale_color_viridis(option="magma", discrete = T, begin = 0.7) +
  theme_minimal() + 
  theme(
    panel.background = element_rect(fill = "white", colour = "white"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text = element_text(size = 12, colour="black"),
    axis.title.x = element_text(size = 12, colour="black", face = "bold"),
    legend.position = ""
  )

  ## --------------- ##
  # Map
  ## --------------- ##

@@

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(), fill = "white", color =  "grey50",size = 0.1) +
    geom_sf(data = Brazil_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = Brazil_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text",
             x =-135,
             y = -69,
             label = "Participation (%)",
             color="black",
             size=4,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-76,-35,6,48,88),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-135,
             y = -85,
             label = "Time of Emergence",
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-79,-39,3,45,87),
             y = -85,
             label = seq(2100,2000,-25), # original
             # label = c(">2100",seq(2075,2000,-25)), # not inluding the > because we dont know
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = c("","","","","")#,
      # direction = -1
    ) +
    # scale_fill_gradientn("",
    #                      limits = c(2000,2100),
    #                      breaks = seq(2000,2100,25),
    #                       labels = c("","","","",""),
    #                      colours = pal
    # ) +
    # geom_hline(yintercept = c(-50,0,50,80)) +
    my_ggtheme_m() +
    theme(
      legend.box.margin = margin(t = -64, l = 229),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line")
    )

@@

  p <- ggdraw() +
    # ToE Latitudinal plot
    draw_plot(Eez_hist, x = 0.873, y = 0.53, width = 0.124, height = 0.37) +
    # Time of Emergence Map
    draw_plot(map, x = 0, y = 0.4, width = 0.95, height = 0.6) +
    # Regional boxplot
    draw_plot(boxplot, x = 0, y = -0.03, width = 1, height = 0.44) +
    # Labels
    draw_plot_label(label = c("A", "B"), 
                      size = 20,
                      x = c(0, 0), 
                      y = c(0.95, 0.46)
      )

@@

Buble_data <- Eez_d_hist %>% 
  filter(metric == "mean_yr") %>% 
  group_by(sau_fishing_entity,tresh) %>% 
  summarise(mean_yr = mean(value)) %>% 
  left_join(Eme_value_data,
            by = c("sau_fishing_entity","tresh")) %>% 
  filter(tresh == "Tresh_one",
         variable == "value") %>% 
  mutate(
    weight_toe = sum_value/mean_yr,
    sum_value_bi = sum_value/1000000000,
    log_value = log10(sum_value_bi)
    ) %>%   # Billion usd
  left_join(Matching_names,
            by = c("sau_fishing_entity","fishing_entity_id")) %>% 
  distinct(sau_fishing_entity,.keep_all = TRUE) %>% 
  filter(!is.na(un_geo_region)) %>% 
  ungroup() %>% 
  mutate(
    sau_fishing_entity = ifelse(sum_value_bi >= 1 & !sau_fishing_entity %in% c("Spain"), paste(sau_fishing_entity,"*",sep = ""),sau_fishing_entity))

@@

# Plot the bubbles!
ggplot(Buble_data) +
  geom_point(
    aes(
      x = mean_yr,
      y = log_value,
      size = n_taxa,
      # colour = un_geo_region,
      shape = un_geo_region
    ),
    alpha = 0.7
  ) +
  # Divisory lines
  geom_vline(xintercept = 2030, color = "grey90", size = 0.5) +
  geom_hline(data = Percentile_value,
             aes(yintercept = x),
             color = "grey90"
  )  +
  geom_label_repel(data = subset(Buble_data, sum_value_bi >= 1),
                   aes(
                     x = mean_yr,
                     y = log_value,
                     label = sau_fishing_entity
                   ),
                   arrow = arrow(length = unit(0.009, "npc"),
                                 type = "closed",
                                 ends = "first"),
                   force = 2,
                   box.padding = 1,
                   fill = "NA"

  ) +
  geom_text(data = Labels_data,
            aes(
              x = x,
              y = y,
              label = label
            ),
            size = 3,
            color = "grey30"
  ) +
  scale_color_viridis(name="Region",
                      discrete = T) +
  scale_x_continuous("Average time of emergence",
                     limits = c(2000,2080),
                     breaks = seq(2000,2080,10)
  ) +
  scale_y_continuous("Fishing revenue (log10)",
                     limits = c(-6,2),
                     breaks = seq(-6,2,2),
                     expand = c(0,0)
  ) +
  scale_size("Number of\nemerging taxa") +
  ggsave("./Figures/bubble_plot.png",
         width = 8,
         height = 8,
         units = "in"
  )

@@

Prop_results %>% 
  filter(variable == "n_per") %>% 
  group_by() %>% 
  summarise(
    median(early,na.rm=T),
    sd(early,na.rm=T)
  )

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  filter(
    variable %in% c("mean_eez","n_per")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

n_taxa_data <- Prop_results %>% 
  filter(variable == "n_spp") %>%
  select(eez_name,early,mid) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  group_by(sau_fishing_entity,fishing_entity_id) %>% 
  summarise(avrg_spp_per = mean(early,na.rm=T))

n_taxa_map <- World_map %>% 
  left_join(n_taxa_data,
            by = c("sau_fishing_entity","fishing_entity_id")
            )

mean(n_taxa_data$avrg_spp_per,na.rm=T)

@@

# gc()# clean ram

time <- "per_mid"
# time <- "per_early"

@@

Prop_map <- ggplot() +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,col = "white") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_point(data = subset(Map_data, time_step == time & per_plot < 0),
             aes(start_lon,
                 start_lat
             ),
             size = 0.05,
             col = "gray80",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_plot > 0),
            aes(X,
                Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 0.3,
            lineend = "round",
            arrow = arrow(length = unit(0.008, "npc"),
                          ends = "first"),
            show.legend = NA) +
  # Closeup Rectangles 
  geom_rect(data=Rectangles,
            aes(xmin=x1, 
                xmax=x2,
                ymin=y1,
                ymax=y2),
            color="grey50", 
            fill = NA,
            linetype = "dashed"
            ) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Stock-Share Ratio Gain \nand taxa change (%)",
    limits = c(0,max(Map_data$per_plot)),
    breaks = seq(0,max(Map_data$per_plot),10)#,
    # option="magma",
    # direction = -1
  ) +
  scale_fill_viridis(
    name="Stock-Share Ratio Gain \nand taxa change (%)",
    limits = c(0,max(Map_data$per_plot)),
    breaks = seq(0,max(Map_data$per_plot),10)#,
    # alpha = 0.8
    # option="magma",
    # direction = -1
  ) #+
  # ggsave("./Figures/fig_sup_1.png",
  # width = 12,
  # height = 8,
  # units = "in"
  # )

@@

Lat_am_map <- ggplot() +
  geom_sf(data = Lat_am_eez, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,col = "white") +
  geom_point(data = subset(Lat_am_data, time_step == time & per_plot < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Lat_am_paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-100, -55),ylim = c(9, 30)) + 
  labs(x = "", y = "") +
  scale_x_continuous(breaks = seq(-100,60,10)) +
  scale_y_continuous(breaks = seq(10,30,10)) +
  my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid.major =  element_line(color = "white")
        ) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Lat_am_data$per_plot)),
    breaks = seq(0,max(Lat_am_data$per_plot),10),
    # option="magma",
    # direction = -1
  )+
  scale_fill_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Lat_am_data$per_plot)),
    breaks = seq(0,max(Lat_am_data$per_plot),10),
    # option="magma",
    # direction = -1
  );Lat_am_map

@@

# Med plot
Med_map <- ggplot() +
  geom_sf(data = Med_eez, size = 0.5, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,col = "white") +
  geom_point(data = subset(Med_data, time_step == time & per_plot < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Med_paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-3, 35),ylim = c(30, 45)) +
  labs(x = "", y = "") +
  scale_x_continuous(breaks = seq(-5,35,10)) +
  scale_y_continuous(breaks = seq(30,50,5)) +
  my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid.major =  element_line(color = "white")
        ) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Med_data$per_plot)),
    breaks = seq(0,max(Med_data$per_plot),5),
    # option="magma",
    # direction = -1
  )+
  scale_fill_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Med_data$per_plot)),
    breaks = seq(0,max(Med_data$per_plot),5),
    # option="magma",
    # direction = -1
  )#;Med_map

@@

@@

@@

# Possible explanatory variables

>>>>

World_eez_sf %>% 
  filter(str_detect(eez_name,"Russia")) %>% 
  ggplot() +
  geom_sf() +
  aes(fill = eez_name)

@@

#### Both plots for tresh one
#  Embarrasing coding Juliano!

ggplot() +
  geom_area(data = subset(plot_data, level == "stock"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            # alpha= 1,
            size=0.5,
            colour="black"
  )  +
  geom_area(data = subset(plot_data, level == "eez"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            # alpha= 0.8,
            size=0.5,
            colour="black"
  )  +
  # Shameslly plot it again to fix colors
  geom_area(data = subset(plot_data, level == "stock" & my_facet == "Percentage (%)"),
            aes(
              x = as.numeric(taxon_emer),
              # x = reorder(as.numeric(taxon_emer),level),
              y = value,
              fill = level
            ),
            # alpha= 1,
            size=0.5,
            colour="black"
  )  +
  # geom_line(data = subset(plot_data, metric == "com_sum"),
  #           aes(
  #             x = as.numeric(taxon_emer),
  #             y = total,
  #             fill = level
  #           ),
  #           colour="grey30",
  # )  +
  # geom_text(data = subset(plot_data, metric == "com_sum"),
  #           aes(
  #             x = 2037,
  #             y = total+5,
  #             label = label
  #           ),
  #           size = 3,
  #           colour="grey30",
  #           hjust=0.6,
  # )  +
  facet_wrap(~my_facet,
             scales = "free") + 
  scale_y_continuous("",
                     expand = c(0,0)
                     ) +
  scale_x_continuous("Time of emergence",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     label = c(seq(2000,2075,25),">2100"),
                     expand = c(0, 0)
  ) +
  my_ggtheme_p() +
  theme(
    legend.position = "right",
    strip.text.x = element_blank(),
    panel.spacing = unit(3, "lines") # space between plots
  ) +
  guides(fill=guide_legend(title= "Level", reverse=FALSE)) +
  scale_fill_viridis(discrete = T,
                     begin = 0.1, 
                     end = 0.7,
                     labels = c("EEZs","Stocks")
  ) +
  ggsave("./Figures/cumu_per_freq.png",
  width = 10,
  height = 5,
  units = "in"
  )

@@

# Eez_hist <- Eme_Res %>% 
#   group_by(eezid,eez_name = sf_eez_name) %>% 
#   left_join(Eez_centroid) %>% 
#   filter(tresh == tresh_list[i]) %>% 
#   group_by(latitude) %>% 
#   summarise(
#     number = n()
#   ) %>% 
#   group_by() %>% 
#   mutate(RMean = rollmean(x = number, 
#                           10, 
#                           align = "center", 
#                           fill = number
#   )
#   ) %>% 
#   mutate(lab="lab") %>% 
#   ggplot() +
#   geom_area(
#     aes(
#       x = latitude,
#       y = RMean,
#       fill = lab,
#       color = lab
#     )
#   ) +
#   coord_flip() +
#   scale_x_continuous("",
#     limits = c(-50,80),
#     breaks = c(-50,0,50,80)
#   ) +
#   scale_y_continuous(
#     "Emerging stocks",
#     limits = c(0, 124),
#     breaks = c(0,62,124)
#     
#   ) +
#   scale_fill_viridis(option="magma", discrete = T, begin = 0.7) +
#   scale_color_viridis(option="magma", discrete = T, begin = 0.7) +
#   theme_minimal() + 
#   theme(
#     panel.background = element_rect(fill = "white", colour = "white"),
#     panel.grid.major.y = element_blank(),
#     panel.grid.minor.y = element_blank(),
#     panel.grid.major.x = element_blank(),
#     panel.grid.minor.x = element_blank(),
#     axis.text.y = element_blank(),
#     axis.ticks.y = element_blank(),
#     axis.text = element_text(size = 12, colour="black"),
#     axis.title.x = element_text(size = 12, colour="black", face = "bold"),
#     legend.position = ""
#   )
#   
  ## --------------- ##
  # Map
  ## --------------- ##

@@

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(), fill = "white", color =  "grey50",size = 0.1) +
    geom_sf(data = Brazil_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = Brazil_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text",
             x =-135,
             y = -69,
             label = "Participation (%)",
             color="black",
             size=4,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-72,-35,5,46,82),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-135,
             y = -85,
             label = "Time of Emergence",
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-79,-39,2,42,81),
             y = -85,
             label = seq(2100,2000,-25), # original
             # label = c(">2100",seq(2075,2000,-25)), # not inluding the > because we dont know
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = c("","","","","")#,
      # direction = -1
    ) +
    # scale_fill_gradientn("",
    #                      limits = c(2000,2100),
    #                      breaks = seq(2000,2100,25),
    #                       labels = c("","","","",""),
    #                      colours = pal
    # ) +
    # geom_hline(yintercept = c(-50,0,50,80)) +
    my_ggtheme_m() +
    theme(
      legend.box.margin = margin(t = -64, l = 249),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line")
    )

@@

  p <- ggdraw() +
    # ToE Latitudinal plot
    # draw_plot(Eez_hist, x = 0.873, y = 0.53, width = 0.124, height = 0.37) +
    # Time of Emergence Map
    draw_plot(map, x = 0, y = 0.4, width = 1, height = 0.6) +
    # Regional boxplot
    draw_plot(boxplot, x = 0, y = -0.03, width = 1, height = 0.44) +
    # Labels
    draw_plot_label(label = c("A", "B"), 
                      size = 20,
                      x = c(0, 0), 
                      y = c(0.95, 0.46)
      )

@@

Buble_data <- Eez_d_hist %>% 
  filter(metric == "mean_yr") %>% 
  group_by(sau_fishing_entity,tresh) %>% 
  summarise(mean_yr = mean(value)) %>% 
  left_join(Eme_value_data,
            by = c("sau_fishing_entity","tresh")) %>% 
  filter(tresh == "Tresh_one",
         variable == "value") %>% 
  mutate(
    weight_toe = sum_value/mean_yr,
    sum_value_bi = sum_value/1000000000,
    log_value = log10(sum_value_bi)
    ) %>%   # Billion usd
  left_join(Matching_names,
            by = c("sau_fishing_entity","fishing_entity_id")) %>% 
  distinct(sau_fishing_entity,.keep_all = TRUE) %>% 
  filter(!is.na(un_geo_region)) %>% 
  ungroup()# %>%  # no more asterisk
  # mutate(
  #   sau_fishing_entity = ifelse(sum_value_bi >= 1 & !sau_fishing_entity %in% c("Spain"), paste(sau_fishing_entity,"*",sep = ""),sau_fishing_entity))

@@

# Plot the bubbles!
ggplot(Buble_data) +
  geom_point(
    aes(
      x = mean_yr,
      y = log_value,
      size = n_taxa,
      colour = un_geo_region,
      shape = un_geo_region
    ),
    alpha = 0.7
  ) +
  # Divisory lines
  geom_vline(xintercept = 2030, color = "grey90", size = 0.5) +
  geom_hline(data = Percentile_value,
             aes(yintercept = x),
             color = "grey90"
  )  +
  # right side labels
  geom_label_repel(data = subset(Buble_data, mean_yr > 2035 & sum_value_bi >= 1),
                  aes(
                    x = mean_yr,
                    y = log_value,
                    label = sau_fishing_entity
                  ),
                  arrow = arrow(length = unit(0.009, "npc"),
                                type = "closed",
                                ends = "first"),
                  force = 2,
                  box.padding = 0.2,
                  fill = "NA",
                  nudge_x = 2050 + subset(Buble_data, mean_yr > 2035 & sum_value_bi >= 1)$mean_yr,
                  segment.size  = 0.2,
                  segment.color = "grey50",
                  direction     = "y",
                  hjust         = 1
  ) +
  # right side labels
  geom_label_repel(data = subset(Buble_data, mean_yr < 2035 & sum_value_bi >= 1),
                  aes(
                    x = mean_yr,
                    y = log_value,
                    label = sau_fishing_entity
                  ),
                  arrow = arrow(length = unit(0.009, "npc"),
                                type = "closed",
                                ends = "first"),
                  force = 1,
                  box.padding = 0.2,
                  fill = "NA",
                  nudge_x = 2010 - subset(Buble_data, mean_yr < 2035 & sum_value_bi >= 1)$mean_yr,
                  segment.size  = 0.2,
                  segment.color = "grey50",
                  direction     = "y",
                  hjust         = 1
  ) +
  geom_text(data = Labels_data,
            aes(
              x = x,
              y = y,
              label = label
            ),
            size = 3,
            color = "grey30"
  ) +
  scale_shape("Region") +
  scale_color_viridis(name="Region",
                      discrete = T) +
  scale_x_continuous("Average time of emergence",
                     limits = c(2000,2080),
                     breaks = seq(2000,2080,10)
  ) +
  scale_y_continuous("Fishing revenue (log10)",
                     limits = c(-6,2),
                     breaks = seq(-6,2,2),
                     expand = c(0,0)
  ) +
  scale_size("Number of\nemerging stock") +
  ggsave("./Figures/bubble_plot.png",
         width = 8,
         height = 8,
         units = "in"
  )

@@

Prop_results %>% 
  filter(variable == "n_spp") %>% 
  group_by() %>% 
  summarise(
    median(early,na.rm=T),
    sd(early,na.rm=T)
  )

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  # gather("variable","value",per_early:per_early_plot) %>% 
  filter(
    variable %in% c("mean_eez","n_spp")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

# Total number of transboundary stocks per EEZ
n_trans_eez <- Transboundary_spp %>% 
  group_by(eez_name) %>% 
  summarise(
    n_trans = unique(length(taxon_key))
  )

# Estimate the percentage changing
n_taxa_data <- Prop_results %>% 
  filter(variable == "n_spp") %>%
  select(eez_name,early,mid) %>% 
  left_join(n_trans_eez) %>% 
  # mutate(per = (early/n_trans)*100) %>% 
  mutate_at(vars(early,mid),
            .funs = ~(./n_trans)*100) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  select(sau_fishing_entity,fishing_entity_id,early,mid) %>% 
  gather("time_step","avrg_spp_per",early:mid) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,time_step) %>%
  summarise(avrg_spp_per = mean(avrg_spp_per,na.rm=T)) %>% 
  mutate(time_step = ifelse(time_step == "early","per_early","per_mid"))

# Paper numbers
mean(n_taxa_data$avrg_spp_per,na.rm=T)
sd(n_taxa_data$avrg_spp_per,na.rm=T)

# Included in map
n_taxa_map <- World_map %>% 
  full_join(n_taxa_data,
            by = c("sau_fishing_entity","fishing_entity_id")
            )

@@

time_sets <- c("per_early","per_mid")
# i = 1
for(i in 1:2){
  gc()# clean ram

  time <- time_sets[i]

@@

  Prop_map <- ggplot() +
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
    geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") + # created for figure 2
    geom_point(data = subset(Map_data, time_step == time & per_plot < 0),
               aes(start_lon,
                   start_lat
               ),
               size = 0.05,
               col = "gray80",
               shape = 20,
               stroke = 1.5) +
    geom_path(data = subset(paths, time_step == time & per_plot > 0),
              aes(X,
                  Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 0.3,
              lineend = "round",
              arrow = arrow(length = unit(0.008, "npc"),
                            ends = "first"),
              show.legend = NA) +
    # Closeup Rectangles 
    geom_rect(data=Rectangles,
              aes(xmin=x1, 
                  xmax=x2,
                  ymin=y1,
                  ymax=y2),
              color="grey50", 
              fill = NA,
              linetype = "dashed"
    ) +
    my_ggtheme_m() +
    scale_colour_viridis(
      name="Stock share ratio gain \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10)#,
      # option="magma",
      # direction = -1
    ) +
    scale_fill_viridis(
      name="Stock share ratio gain \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10),
      # alpha = 0.8
      # option="magma",
      # direction = -1
    ) #+
  # ggsave("./Figures/fig_sup_1.png",
  # width = 12,
  # height = 8,
  # units = "in"
  # )

@@

  Lat_am_map <- ggplot() +
    geom_sf(data = Lat_am_eez, size = 0.1, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,col = "white") +
    geom_point(data = subset(Lat_am_data, time_step == time & per_plot < 0 ),
               aes(start_lon,
                   start_lat,
                   col = per_plot),
               size = 1,
               col = "gray30",
               shape = 20,
               stroke = 1.5) +
    geom_path(data = subset(Lat_am_paths, time_step == time & per_plot > 0),
              aes(X, Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 1,
              arrow = arrow(length = unit(0.05, "npc"),
                            ends = "first"),
              show.legend = NA) +
    coord_sf(xlim = c(-100, -55),ylim = c(9, 30)) + 
    labs(x = "", y = "") +
    scale_x_continuous(breaks = seq(-100,60,10)) +
    scale_y_continuous(breaks = seq(10,30,10)) +
    my_ggtheme_m() +
    theme(legend.position = "",
          panel.background = element_rect(fill = "white", color = "white"),
          panel.grid.major =  element_line(color = "white")
    ) +
    scale_colour_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Lat_am_data$per_plot)),
      breaks = seq(0,max(Lat_am_data$per_plot),10),
      # option="magma",
      # direction = -1
    )+
    scale_fill_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Lat_am_data$per_plot)),
      breaks = seq(0,max(Lat_am_data$per_plot),10),
      # option="magma",
      # direction = -1
    )

@@

  # Med plot
  Med_map <- ggplot() +
    geom_sf(data = Med_eez, size = 0.5, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") + # created for figure 2
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,col = "white") +
    geom_point(data = subset(Med_data, time_step == time & per_plot < 0 ),
               aes(start_lon,
                   start_lat,
                   col = per_plot),
               size = 1,
               col = "gray30",
               shape = 20,
               stroke = 1.5) +
    geom_path(data = subset(Med_paths, time_step == time & per_plot > 0),
              aes(X, Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 1,
              arrow = arrow(length = unit(0.05, "npc"),
                            ends = "first"),
              show.legend = NA) +
    coord_sf(xlim = c(-3, 35),ylim = c(30, 45)) +
    labs(x = "", y = "") +
    scale_x_continuous(breaks = seq(-5,35,10)) +
    scale_y_continuous(breaks = seq(30,50,5)) +
    my_ggtheme_m() +
    theme(legend.position = "",
          panel.background = element_rect(fill = "white", color = "white"),
          panel.grid.major =  element_line(color = "white")
    ) +
    scale_colour_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Med_data$per_plot)),
      breaks = seq(0,max(Med_data$per_plot),5),
      # option="magma",
      # direction = -1
    )+
    scale_fill_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Med_data$per_plot)),
      breaks = seq(0,max(Med_data$per_plot),5),
      # option="magma",
      # direction = -1
    )#;Med_map

@@

## Sensitivity analysis

Testing different Per values for the centroids

```{r data_loading, eval = T, echo = F}

# Get taxon list
Taxon_list_sens <- list.files(my_path("R",extra_path = "Toe_Sens_per/Emergence_2005_p20"))

# clean names for function
Taxon_list_sens <- gsub("_.*","",Taxon_list_sens)

@@

### Arctic and Brasil missing species

```{r arctic, eval = F, echo =F}

@@

Arctic <- c("Canada (Arctic)","USA (Alaska, Arctic)", "Russia (Laptev to Chukchi Sea)")

can_us_arctic <- Transboundary_spp %>% 
  filter(eez_name == "Canada (Arctic)",
         eez_neighbour == "USA (Alaska, Arctic)")

arctic_spp <- Transboundary_spp %>% 
  filter(eez_name %in% Arctic,
         eez_neighbour %in% Arctic)
